Periodograms for Multiband Astronomical Time Series

### 2015-01-28 writeup/paper.tex
minor edits in Conclusions

Looking forward to future variable star catalogs from PanSTARRS, DES, and LSST, there are two important constraints that any analysis method must meet: the methods must be able to cope with heterogeneous and noisy observations through multiple band-passes, and the methods must be fast enough to be computable on millions or even billions of objects.
The multiband method, through its combination of flexibility and model simplicity, meets the first: as shown above, it performs well in the case of sparsely-sampled multiband data.
It also meets the second constraint: it consists of a fast linear model at each frequency, compared to a sliding-window model in the case of supersmoother, a nonlinear optimization in the case of template-fitting, and a Markov Chain Monte Carlo in the case of CARMA models.
In our own benchmarks, we found the multiband method to be several times faster than the single-band supersmoother approach, and several orders of magnitude faster than the template fitting approach.
This suggests that the multiband periodogram could have an important role to play in the analysis of variable stars in future surveys.

>>>>

Looking forward to future variable star catalogs from PanSTARRS, DES, and LSST, there are two important constraints that any analysis method must meet: the methods must be able to cope with heterogeneous and noisy observations through multiple band-passes, and the methods must be fast enough to be computable on millions or even billions of objects.
The multiband method, through its combination of flexibility and model simplicity, meets the first: as shown above, it performs well in the case of sparsely-sampled multiband data.
It also meets the second constraint: it consists of a fast linear model at each frequency, compared to a sliding-window model in the case of supersmoother, a nonlinear optimization in the case of template-fitting, and a Markov Chain Monte Carlo in the case of CARMA models.
In our own benchmarks, we found the multiband method to be several times faster than the single-band supersmoother approach, and several orders of magnitude faster than the template fitting approach.
This suggests that the multiband periodogram could have an important role to play in the analysis of variable stars in future surveys
and we make our tools publicly available on GitHub.
